\documentclass{article}

\title{Class Website CSS Design Contest}
\date{}

\begin{document}

\maketitle
\vspace{-15 mm}

Due Thursday, August 30th.

\vspace{5 mm}
Make a new design for the class website.  It doesn't need to be elaborate, but it should look more interesting than the current one.

\vspace{5 mm}

Next week, I will post all of your submissions, and you will be able to vote on which one the class website keeps as its default appearance.
\vspace{5 mm}

Getting started:
\begin{enumerate}
\item Go to the class webpage, and save the page to your desktop.  You can do this by clicking ``save'' in the ``file'' menu in your browser, or by using control-s.  Save it as \texttt{classpage.html}.
\item Click on the link for the template stylesheet on the website and save it on your desktop as \texttt{stylesheet.css}
\item Open the \i{file you saved} in a browser by typing \texttt{file:///} and then the filepath of the \texttt{classpage.html} file into your browser bar.  It will look something like \texttt{file:///home/ruthie/Desktop/classpage.html}.
\item Open \texttt{template\_stylesheet.css} in a text editor.
\item Uncomment the contents of the \texttt{body} selector by removing the \texttt{/*} and the \texttt{*/}.
\item Reload the file you opened in your browser.  It should now be purple.  If it is not purple, something is wrong.  Reexamine everything you just did-- are both \texttt{classpage.html} and \texttt{stylesheet.css} saved on your desktop?  Are you looking at the saved file and not the actual class webpage?  If you still can't figure out what's going wrong, ask me.
\item If it did work, awesome, you are now ready to start editing the stylesheet however you want!  Feel free to experiment.  Look for things you can do on the W3C website (links are on the class webpage), or look at webpages you like to see how they're styled.

\end{enumerate}

Notes:
\begin{itemize}
\item You shouldn't have to modify the HTML at all.  If you think a particular change to the HTML would allow you to do something with the style that you can't do otherwise, ask me before making the change. 
\item You should turn in this assignment by {\bf emailing} your stylesheet to me.
\end{itemize}

\end{document}
