\documentclass{article}
\title{Protocol Research Project}
\begin{document}

\maketitle
\section{Introduction}
There are many more internet protocols than we can cover in this class.  In this project, you will research and present on one of the ones that we will not cover in depth.

\section{Requirements}
Your project will consist of 
\begin{enumerate}
\item The answers to the questions in the ``Questions'' section in written format.  Each question needs at least a sentence answer, and depending on your topic, some will require as much as a paragraph.  It is up to you to determine how much text you need to answer each question completely.
%so your report should look like 1. [answer to first question]
\item A presentation to the class including the answers to the same questions.
\item A demonstration of the protocol in some form. 
\end{enumerate}

\hspace{10mm}

\section{Questions}
Your report and presentation should include the following information:
\begin{enumerate}
\item In human terms, what this protocal does.
\item What layer of the ip suite does your protocol belong to (link layer, internet layer, transport layer, or application layer)?
\item Specification the protocol (for complex protocols, you can give a summary).  In other words, how does the protocol work in technical terms?
\item What other protocols that serve the same purpose, if any, exist or have existed?  If there are no other similar protocols, what would we do if this protocol didn't exist?
\item When is this protocol used instead if its alternatives (either other protocols, or what we would do if the protocol didn't exist)?
\item What are the advantages and disadvantages of the way this protocol was designed?
\end{enumerate}

\section{Due dates}
\begin{itemize}
\item Email me by the beginning of class this Tuesday ({\bf July 16th}) to claim a topic.

\item On Thursday ({\bf July 18th}), I will check in with each of you.  At that time you should have a draft of the written part and know how you are going to do your demonstration.

\item Presentations will be made next Tuesday ({\bf July 23rd}).

\end{itemize}

\section{Advice}
\begin{itemize}
\item Your presentation should include either slides or diagrams drawn on the white board.  You shouldn't just stand at the front of the class talking.
\item Dry-run your presentation, timing yourself at least once.  Make sure your dry-run includes your demonstration.
\end{itemize}

\section{Possible Topics}
\begin{itemize}
\item Time Division Multiplexing (Media access control)
\item Token ring (Media access control)
\item ALOHA (Media access control)
\item IEEE 802.11 (local wireless network link layer protocol)
\item IP Multicasting
\item IPv6
\item UDP (User Datagram Protocol)
\item ICMP (Internet Control Message Protocol)
\item telnet
\item SMTP (Simple Mail Transfer Protocol, aka email)
\item SSH (Secure Shell)
\item LPD (Line Printer Daemon)
\item DNS (Domain Name Service)
\item IRC (Internet Relay Chat)
\item NTP (Network Time Protocol)
\end{itemize}
\end{document}
