\documentclass{article}

\title{Website Project}

\begin{document}
\maketitle

\section{Goal}
The goal of this project is to set up a static website and deploy it on the actual internet.  You will get a chance to use the technology we've discussed (and are about to discuss) in real life.  You'll learn to debug a system in order to acquire a polished final product.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Requirements}
\begin{enumerate}
\item Your website should have at least three separate pages (three HTML files).
\item At least 15 different HTML tags used somewhere in those three pages.
\item At least 5 CSS classes, and be .
\item At least 30 lines of javascript.  Javascript can be used to augment functionality, or to add stuff like popup dialogues or color changing elements that just look cool.
\item No javascript errors, links that give you HTTP 404 errors, or other broken functionality.  That is, whatever you set up should work.
\end{enumerate}


\subsection{Plan}
As of next Monday, I want a plan answering each of the following questions:

\begin{enumerate}
\item What will your website be about/do?
\item How are you going to use javascript?
\item Give a rough schedule for working on your project.  When do you want to have what done?
\end{enumerate}

The project will be due on the last Monday of class (August 12th).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Deploying your Website}
We will be deploying our websites using nearlyfreespeech.net.  You can use nearlyfrespeech.net as you develop your website.
Nearly Free Speech is a pay-as-you-go web hosting service.  You pay per GB transferred, per GB of storage and for several types of add-ons (like a DNS name).  Junction will give each of you a \$10 startup fund.  If you are frugal, this should be enough to put a website up and keep it up for years.

\subsection*{Logistics}
As soon as you can, follow these instructions to get funding from Junction:

\begin{enumerate}
\item Make an account on nearlyfreespeech.net.
\item Log in and click the ``accounts'' tab.  You should have one account, with status ``free trial''.
\item Email me your username and the number of that ``free trial'' account.
\end{enumerate}
A new account comes with \$0.02 of credit, so you should be able to use your account right away, even before it gets credit from Junction.

\subsection*{Obligatory warning about posting things on the internet}
Unlike your facebook, whatever you post online will be 100\% public.  You should be careful about posting personal information such as your address on the internet.  If you choose to post an email address, you should post it in some form like ``yourname at gmail dot com'' to prevent bots from picking it up and sending you spam.  You should also be careful about posting anything that you think you don't want a future employer to know unless you are publishing anonymously.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Ideas}
You probably want to think about what you want the content of your webpage to be.  Here is a (non-exhaustive) list of ideas:
\begin{itemize}
\item A personal website
\item A blog
\item A website for posting personal artwork/writing/photography/music.
\item A website for a group you're part of
\item An informational website about something you know about
\end{itemize}

\end{document}
